---
title: "R Notebook"
output: html_notebook
---

Atempting to understand how pasrse works ...

```{r}
require()
cat(readLines("./scripts/001-simple.R"), sep = "\n")
```

```{r}
parse("./scripts/001-simple.R")
```

Alright ... so it returns an expression ...
which can be converted to a list

```{r}
parsed_file <- parse("./scripts/001-simple.R")

as.list(parsed_file)

```

and ... what is each element of the list ?

```{r}
lapply(as.list(parsed_file), class)
```

Thats interesting ... that means that assignments can be found as elements with class `<-`

what if we call as a list all elements of the former ...

```{r}
lapply(as.list(parsed_file), as.list)
```


so hypothetically ... if we subsetted all elements of class `<-` and got
element 2, we would get the defined variable.


```{r}
is_assign <- "<-" == sapply(as.list(parsed_file), class)

lapply(as.list(parsed_file)[is_assign], function(...) ...[[2]])
```

and element 3 ... value that was assigned

```{r}
lapply(as.list(parsed_file)[is_assign], function(...) ...[[3]])
lapply(as.list(parsed_file)[is_assign], function(...) class(...[[3]]))

```

One could go down the rabbit-hole and make each of those a list ...

```{r}
lapply(as.list(parsed_file)[is_assign], function(...) as.list(...[[3]]))
```

```{r}
unlist(lapply(as.list(parsed_file)[is_assign], function(...) as.list(...[[3]]))) %>% lapply(class)

```


```{r}
unlist_calls <- function(...) {
    tmp <- as.list(...)
    for (i in seq_along(tmp)) {
        if (is.call(tmp[[i]])) {
            tmp[[i]] <- unlist_calls(tmp[[i]])
        }
    }
    return(tmp)
}


```


```{r}
lapply(as.list(parsed_file)[is_assign], function(...) ...[[3]])
lapply(as.list(parsed_file)[is_assign], function(...) class(...[[3]]))


unlist(as.list(str2lang("foo(1,2,3,4,5)")))
rapply()
```


After all of this i found out that rapply can recursively apply a function...
such as as.list

```{r}
rapply(parsed_file, as.list, how = "list") %>% 
    rapply(., as.list, how = "list") %>% 
    unlist() %>% 
    lapply(class)
```

So we can make a lot of intermediate functions ...

```{r}
unlist_call <- function(element) {
    if (is.call(element)) {
        elem_list <- as.list(element)
        ret <- list(
            call_name = elem_list[[1]],
            arguments = elem_list[-1])
        return(ret)
    } else {
        return(element)
    }
}

recunlist_calls <- function(my_list) {
    tmp <- rapply(my_list, unlist_call, how = "list")
    
    if (identical(tmp, my_list)) {
        return(tmp)
    } else {
        recunlist_calls(tmp)
    }
}

parse_assign <- function(my_list) {
    assigned_var <- my_list[[1]]
    assigned_val <- my_list[-1]
    
    return(list(assigned_var = assigned_var, 
                assigned_val = assigned_val))
    
}

get_global_df <- function(parsed_file) {
    tmp <- recunlist_calls(parsed_file) %>% 
        purrr::transpose() %>% 
        as_tibble() %>% 
        mutate(call_name = as.character(call_name)) %>% 
        filter(call_name == "`<-`") %>%
        mutate(arguments = purrr::map(arguments, parse_assign))  %>%
        .[[2]] %>% 
        purrr::transpose() %>% 
        as_tibble() %>% 
        mutate(assigned_var = as.character(assigned_var))
    
    tmp[[2]] <- lapply(tmp[[2]], replace_singlets)
    return(tmp)
}

get_globals <- function(parsed_file) {
    
    ret <- get_global_df(parsed_file)
    
    return(ret[["assigned_var"]])
}


get_globals(parsed_file)
get_global_df(parsed_file)

get_dependencies <- function(parsed_file) {
    global_df <- get_global_df(parsed_file)
    
    var_names <- global_df[["assigned_var"]]
    
    global_df[["Dependencies"]] <- lapply(
        global_df[["assigned_val"]], 
        FUN = unlist, 
        recursive = FALSE, 
        use.names = FALSE)

    global_df[["Global_Dependencies"]] <- purrr::map(
        global_df[["Dependencies"]],
        ~ var_names[var_names %in% as.character(.x)])
    
    global_df <- global_df[,c("assigned_var", "Global_Dependencies")]
    colnames(global_df) <- c("To", "From")
    
    unnested_df <- unnest(global_df, cols = c("From"))
    return(unnested_df)
}

replace_singlets <- function(my_list) {
    if (is.list(my_list) & length(my_list) == 1) {
        return(my_list[[1]])
    } else {
        return(my_list)
    }
}
```

and get a graph based on the names ...

```{r}
get_dependencies(parsed_file)

g <- igraph::graph_from_data_frame(get_dependencies(parsed_file))
plot(g)

```

so each element is an expression, the first element of that list is the main function, "<-" for assignment



